Unlocking Accountability: A Mixed-Methods Analysis of Bottom-Up Approaches in Brazilian Public Policy

### 2023-10-27 Scripts/paper.Rmd
added font and font size

---
title: "Unlocking Accountability: A Mixed-Methods Analysis of Bottom-Up Approaches in Brazilian Public Policy"
date: "2023-10-26"
output: pdf_document
author:
- name: Manoel Galdino
  affiliation: Universidade de São Paulo
abstract: "This paper examines the role of accountability in democratic systems, focusing on its impact on public service delivery. Employing mixed methods, we differentiate between information-driven interventions and the mobilization and monitoring efforts of organized Civil Society Organizations (CSOs). We argue that well-organized CSOs, deeply embedded in society and politics, can drive significant policy change. The study evaluates the effectiveness of the Obra Transparente project by Transparência Brasil, engaging 21 local CSOs in South and Southeast Brazil. In contrast to information-centered approaches, this project establishes a network of local CSOs, providing technical support and training for monitoring public school and nursery construction projects. Our findings emphasize the importance of sustained, coordinated efforts by organized civil society. These efforts, involving direct engagement with municipal officials, persistent follow-ups, and on-site visits, lead to more substantial outcomes. This research contributes to understanding how organized civil society mobilization can achieve bottom-up accountability, a crucial aspect of democratic governance. However, contextual variations may limit the effectiveness of CSO interventions."
keywords: "Accountability, Brazil, mixed methods, state capacity, public policy"
---

>>>>

---
title: "Unlocking Accountability: A Mixed-Methods Analysis of Bottom-Up Approaches in Brazilian Public Policy"
date: "2023-10-26"
output: pdf_document
sansfont: Sans Serif
fontsize: 12pt
author:
- name: Manoel Galdino
  affiliation: Universidade de São Paulo
abstract: "This paper examines the role of accountability in democratic systems, focusing on its impact on public service delivery. Employing mixed methods, we differentiate between information-driven interventions and the mobilization and monitoring efforts of organized Civil Society Organizations (CSOs). We argue that well-organized CSOs, deeply embedded in society and politics, can drive significant policy change. The study evaluates the effectiveness of the Obra Transparente project by Transparência Brasil, engaging 21 local CSOs in South and Southeast Brazil. In contrast to information-centered approaches, this project establishes a network of local CSOs, providing technical support and training for monitoring public school and nursery construction projects. Our findings emphasize the importance of sustained, coordinated efforts by organized civil society. These efforts, involving direct engagement with municipal officials, persistent follow-ups, and on-site visits, lead to more substantial outcomes. This research contributes to understanding how organized civil society mobilization can achieve bottom-up accountability, a crucial aspect of democratic governance. However, contextual variations may limit the effectiveness of CSO interventions."
keywords: "Accountability, Brazil, mixed methods, state capacity, public policy"
---
